Acid-induced protein gels: from gelation to stress-induced failure

### 2015-06-03 creep_beamer.tex
Référence du PRL en plus du Arxiv
Talk Zurich Add snapshot for creep experiments

\begin{frame}{Creep and yielding}
Just accepted in PRL, \textit{ArXiv 1401.8234}

\bigskip
\structure{Merciless yoghurt breakers}

@@

>>>>

\begin{frame}{Merciless yoghurt breakers}
\textit{Leocmach et al. PRL 113, 038303 (2014), \footnotesize ArXiv 1401.8234}

@@

\begin{frame}{The yoghurt creep experiment}
\includegraphics[width=\textwidth]{creep/Fig3}
\begin{center}\tikzsetnextfilename{creep_xp_snapshot}
\begin{tikzpicture}
\begin{groupplot}[
	group style={
		group name=g, group size=2 by 1,
		horizontal sep=4\baselineskip,
		},
	xmode=log,
	ymode=log,
	xlabel={$t$ (\si{\second})},
	xmin=0.1,
	%restrict x to domain=0.05:3e3,
	]
	\nextgroupplot[ylabel={strain rate $\dot\gamma$ (\si{\per\second})}, ymin=1e-4, ymax=2e-1]
	\addplot[Accent1] table {Y110_300Pa.gdot}; 
	\addplot[Accent2, only marks, mark=o] coordinates {(31, 1.6e-3) (889, 2e-4) (1442, 5.5e-4) (1509, 1.1e-2)};

	\nextgroupplot[
		ylabel={strain $\gamma$},ymin=0.16,ymax=2,
		ytick={0.2, 0.4,0.8,1.6}, yticklabels={0.2, 0.4,0.8,1.6},]
	\addplot[Accent1] table {Y110_300Pa.txt}; 
	\addplot[Accent2, only marks, mark=o] coordinates {(31, 0.37481) (880, 0.70529) (1459, 0.87393) (1526,0.93622)};

\end{groupplot}
\end{tikzpicture}
\end{center}
\end{frame}

### 2015-06-03 talk_Zurich.tex
Talk Zurich Add snapshot for creep experiments

\institute[E.N.S. Lyon]{Laboratoire de physique, Ecole Normale Sup\'{e}rieure de Lyon}
\title[Yoghurt under stress]{Yoghurt under stress}
\author[M. Leocmach]{Mathieu Leocmach}
\date{16 January 2015}
\titlegraphic{
	\includegraphics[height=2\baselineskip,clip=true, trim=6mm 14mm 6mm 0]{NEW-Logo-ERC-OUTLINE}\quad
	\includegraphics[height=2\baselineskip]{logo_ums_grand}\quad
	\includegraphics[height=2\baselineskip]{CNRSfilaire-Q}\quad
	\includegraphics[height=2\baselineskip]{logo_ens-lyon}
	}

@@

\include{parcourt}

@@

\section*{Wrinkling}

%\tikzset{external/force remake}
\begin{frame}{Over-acidification: Faster but weaker}
\tikzsetnextfilename{gelation_GDL}
\begin{tikzpicture}
\begin{axis}[
	height=0.8\textheight,
	width=\textwidth,
	xlabel={time (h)}, ylabel={$G^\prime$ (\si{\pascal})},
	cycle list name=earthy,
	no marks,
	xmin=0, xmax=20,ymin=0,
	]
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL1_Y265.prise} node[anchor=base west] {1\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL1.25_Y277.prise} node[anchor=base west] {1.25\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL1.5_Y275.prise} node[anchor=base west] {1.5\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL2_Y268.prise} node[anchor=base west] {2\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL3_Y270.prise} node[anchor=base west] {3\%};
	\addplot table[x expr={\thisrowno{0}/3600}]{cas4_GDL4_Y271.prise} node[anchor=base west, yshift=-0.2em] {4\%};
\end{axis}
\end{tikzpicture}

Caseins regain some solubility at low pH.
\end{frame}

\include{plis_beamer}

>>>>

\institute[E.N.S. Lyon]{Laboratoire de physique, Ecole Normale Sup\'{e}rieure de Lyon}
\title[Yoghurt under stress]{Acid-induced protein gels: from gelation to stress-induced failure}
\author[M. Leocmach]{Mathieu Leocmach}
\date{10 June 2015}
\titlegraphic{
	\includegraphics[height=2\baselineskip,clip=true, trim=6mm 14mm 6mm 0]{NEW-Logo-ERC-OUTLINE}\quad
	\includegraphics[height=2\baselineskip]{logo_ums_grand}\quad
	\includegraphics[height=2\baselineskip]{CNRSfilaire-Q}\quad
	\includegraphics[height=2\baselineskip]{logo_ens-lyon}
	}

@@

@@
